---
title: "London Restaurant Scene project- MIBE"
author: "Edoardo Mustarelli"
date: "6/3/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Let's start with the analysis of the files. First I am going to load the libraries necessary, or that may be necessary, to move on with the analysis.

```{r libraries, message=FALSE, warning=FALSE}
# ipak function: install and load multiple R packages.
# check to see if packages are installed. Install them if they are not, then load them into the R session.

ipak <- function(pkg){
new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
sapply(pkg, require, character.only = TRUE)
}

# usage
packages <- c("dplyr", "tidyverse", "tidyr", "here", "magrittr", "purrr", "purrrlyr", "ggplot2", "formattable", "rlist", "gtools", "tm", "SnowballC", "wordcloud","RColorBrewer", "sf", "tmap", "tmaptools", "rgdal", "rgeos", "ggmap", "tidytext", "ggraph", "readr", "htmltools", "webshot")
ipak(packages)

```
```{r datasets}
restaurants_info <- readRDS(file="C:/Users/Edoardo/Desktop/LSU_project/resturants-mibe.rds")
info_delivery <- readRDS(file="C:/Users/Edoardo/Desktop/LSU_project/delivery-mibe.rds")
```
I now want to inspect the dataset regarding the restaurants' information to have a better understanding of what I'm working with.
```{r inspection}
glimpse(restaurants_info)
head(restaurants_info)

```
We can see that the restaurants_info file has 7 variables which are id, name, brand, postcode, neighborhood, rating, and menu item price. We can also see that we have the data for 5,786 restaurants in London.
#### 1 Restaurant Information Analysis

###### 1.1 top 10 neighborhoods by the number of restaurants

```{r}
top10_neighborhoods <- restaurants_info %>%
  group_by(rest_neighborhood) %>%
  filter(!is.na(rest_neighborhood)) %>%
  summarise(number_of_rest=n()) %>%
  arrange(-number_of_rest) %>%
  slice(1:10)
top10_neighborhoods
```
```{r}
top10_neighborhoods$number_of_rest <- as.numeric(top10_neighborhoods$number_of_rest)

top10_neighborhoods %>%
ggplot(aes(reorder(rest_neighborhood, -number_of_rest), number_of_rest, fill=-number_of_rest)) +
  geom_bar(stat = "identity")+
  labs(x = "Neighborhoods", y = "Number of Restaurants", fill="# of rest")+
  ggtitle("Top 10 neighborhoods ranked by number of restaurants")+
  coord_flip()+
  ggsave("10neigh_by_#rest.png")
```

###### 1.2 top 10 neighborhoods by the restaurant review score

```{r}
top10_neig_ratings <- restaurants_info %>%
  group_by(rest_neighborhood) %>%
  summarise_at(vars(rest_rating),list(~mean(., na.rm = TRUE))) %>%
  arrange(-rest_rating) %>%
  slice(1:10)
top10_neig_ratings
```
```{r}
top10_neig_ratings %>%
ggplot(aes(reorder(rest_neighborhood, -rest_rating), rest_rating, fill=-rest_rating)) +
  geom_bar(stat = "identity")+
  labs(x = "Neighborhoods", y = "Average Rating", fill="rating")+
  ggtitle("Top 10 neighborhoods ranked by average ratings of the restaurants")+
  coord_flip()+
  ggsave("10neigh_by_avg_rating.png")
```

```{r}
top_neigh_overall <- inner_join(top10_neighborhoods, top10_neig_ratings)
top_neigh_overall
```
###### 1.3 Top 10 biggest chains

```{r}
top_chains <- restaurants_info %>%
  group_by(rest_brand) %>%
  filter(!is.na(rest_brand)) %>%
  summarise(number_of_spots = n()) %>%
  arrange(-number_of_spots) %>%
  slice(1:10)
top_chains
```
```{r}
top_chains$number_of_spots <- as.numeric(top_chains$number_of_spots)
 webshot::install_phantomjs(force = TRUE)

export_formattable <- function(f, file, width = "100%", height = NULL, 
                               background = "white", delay = 0.2)
    {
      w <- as.htmlwidget(f, width = width, height = height)
      path <- html_print(w, background = background, viewer = NULL)
      url <- paste0("file:///", gsub("\\\\", "/", normalizePath(path)))
      webshot(url,
              file = file,
              selector = ".formattable_widget",
              delay = delay)
    }

FT <- top_chains %>%
  formattable(align = c("l","c"), list(number_of_spots = color_bar(("lightseagreen"))))

export_formattable(FT,"FT.png")

FT

```


###### 1.4 Average menu price and number of items for each restaurant

```{r, message = FALSE, warning = FALSE}
number_of_items_gross <- restaurants_info %>%
  filter(restaurant_id %>%
           map_lgl(any)) %>%
  unnest(rest_menu_item_price)
number_of_items_gross

number_of_items_net <- number_of_items_gross[apply(number_of_items_gross[c(7)],1, function(del) any(!del==0)),]
number_of_items_net
```

```{r}
num_of_items <- number_of_items_net %>%
  group_by(rest_name) %>%
  summarise(num_items_menu = n()) %>%
  arrange(-num_items_menu)
num_of_items
```

```{r}
avg_price <- number_of_items_net %>%
  group_by(restaurant_id, rest_name) %>%
  filter(!is.na(restaurant_id)) %>%
  summarise_at(vars(rest_menu_item_price), list(~mean(.)), na.rm = TRUE)

colnames(avg_price)[3] <- "Avg_price"

avg_price$Avg_price <- sprintf(avg_price$Avg_price, fmt="%#.4f")

avg_price

```

###### 1.5 how many items on the 5 most expensive restaurants' menus?

```{r}
#I want to create a joint dataset between the number of items per menu and the average price

how_many_for_how_much <- left_join(num_of_items, avg_price)

how_many_for_how_much$Avg_price <- as.numeric(how_many_for_how_much$Avg_price)

most_expensive <-  how_many_for_how_much %>%
  arrange(-Avg_price) %>%
  slice(1:5)
most_expensive

```

```{r}
most_expensive %>%
ggplot(aes(reorder(rest_name, num_items_menu), num_items_menu, fill=-Avg_price)) +
  geom_bar(stat = "identity")+
  labs(x = "Name", y = "# of items", fill="avg price")+
  ggtitle("5 most expensive restaurants with relative number of items")+
  coord_flip()+
  ggsave("who_howmuch_howmany.png")
```

From this last graph we can observe how there is almost an inverse relationship between the number of items listed on the menus and the average price. As a matter of fact, the two most expensive restaurants also happen to be the ones with less items on their menus. But we can also see that 4/5 of these ase catering services.

###### 1.6 how many items on the 5 mleast expensive restaurants' menus?

```{r}
least_expensive <-  how_many_for_how_much %>%
  arrange(Avg_price) %>%
  slice(1:5)
least_expensive
```
```{r}
least_expensive %>%
ggplot(aes(reorder(rest_name, num_items_menu), num_items_menu, fill=-Avg_price)) +
  geom_bar(stat = "identity")+
  labs(x = "Name", y = "# of items", fill="avg price")+
  ggtitle("5 least expensive restaurants with relative number of items")+
  coord_flip()+
  ggsave("who_howlittle_howmany.png")
```

```{r}
all_prices <- full_join(most_expensive, least_expensive)

all_prices %>%
ggplot(aes(reorder(rest_name, num_items_menu), num_items_menu, fill=-Avg_price)) +
  geom_bar(stat = "identity")+
  labs(x = "Name", y = "# of items", fill="avg price")+
  ggtitle("5 most & least expensive restaurants with relative number of items")+
  coord_flip()+
  ggsave("all_prices.png")
```


#### 2 Restaurants Delivery Times Analysis

```{r}
colnames(info_delivery)[1] <- "restaurant_id"

complete_rest_data <- left_join(info_delivery, restaurants_info, by = "restaurant_id")
glimpse(complete_rest_data)

```


###### 2.1 How many neighborhoods does each restaurant deliver to?

```{r}
deliveries_where <- complete_rest_data %>%
  group_by(restaurant_id) %>%
  summarise(num_place_of_delivery = n())

glimpse(deliveries_where)

```

###### 2.2 Top 15 neighborhoods for number of restaurants served by.

```{r}
deliveries_by <- complete_rest_data %>%
  group_by(neighborhood_name) %>%
  summarise(how_many_deliver = n()) %>%
  arrange(-how_many_deliver) %>%
  slice(1:15)

glimpse(deliveries_by)
```

```{r}
deliveries_by %>%
ggplot(aes(reorder(neighborhood_name, how_many_deliver), how_many_deliver, fill=neighborhood_name)) +
  geom_bar(stat = "identity")+
  labs(x = "Name", y = "# restaurants delivering", fill="avg price")+
  ggtitle("15 top neighborhoods by # of restaurants that deliver there")+
  coord_flip()+
  ggsave("most_served.png")
```

###### 2.3 Average delivery time per restaurant

```{r}
avg_del_time <- complete_rest_data %>%
  group_by(restaurant_id, rest_name, rest_postcode, rest_rating) %>%
  summarise(avg_time = mean(rest_delivery_time_min, na.rm = TRUE))
avg_del_time
```

###### 2.4 Top 20 fastest restaurants.

```{r}
avg_del_time$avg_time <- as.integer(avg_del_time$avg_time)

glimpse(avg_del_time)
```

```{r}
fastest20 <- avg_del_time %>%
  arrange(-avg_time) %>%
  head(20)
fastest20
```

```{r}
export_formattable <- function(f, file, width = "100%", height = NULL, 
                               background = "white", delay = 0.2)
    {
      w <- as.htmlwidget(f, width = width, height = height)
      path <- html_print(w, background = background, viewer = NULL)
      url <- paste0("file:///", gsub("\\\\", "/", normalizePath(path)))
      webshot(url,
              file = file,
              selector = ".formattable_widget",
              delay = delay)
    }

f20 <- fastest20 %>%
  subset(select = -restaurant_id) %>%
  relocate(avg_time, .before = rest_postcode) %>%
  relocate(Ratings = rest_rating, .before = rest_postcode)

FT2 <- f20 %>%
  formattable(align = c("l", "c", "c", "l"), list(avg_time = color_bar(("lightseagreen"))))

export_formattable(FT2,"FT2.png")

FT2
```

#### 3 Open Analysis

By looking at this data one question comes to my mind almost immediately. Are restaurants located in those neighborhoods that are served by the highest number of delivery places?

I start by creating a new data frame that contains the data all the data from the restaurants and their deliveries, but only for the top 10 neighborhoods for number of restaurants. 
```{r}
complete_data_fortified <- inner_join(complete_rest_data, top10_neighborhoods, by = "rest_neighborhood")
complete_data_fortified
```
I now want to calculate how many restaurants deliver to a neighborhood and where they are from.
```{r}
new_ranking <- complete_data_fortified %>%
  group_by(neighborhood_name, rest_neighborhood) %>%
  summarise(how_many_to_and_from = n()) %>%
  arrange(-how_many_to_and_from) %>%
  slice(1:15)
new_ranking
```

I now want to join together the previous set with how many restaurants deliver to each neighborhood (just the 15 neighborhoods with the highest number of restaurants that deliver there)
```{r}
who_delivers <- inner_join(new_ranking, deliveries_by)
who_delivers
```
At this point I am interested in knowing just the number of restaurants that deliver to each neighborhood and from which neighborhood they are.

```{r}
from_where <- who_delivers %>%
  subset(select = c("neighborhood_name", "rest_neighborhood", "how_many_to_and_from"))
from_where
```

```{r}
how_many <- who_delivers %>%
  subset(select = c("neighborhood_name", "rest_neighborhood", "how_many_deliver"))
how_many
```

```{r}
library(reshape)
from_where.m <- melt(from_where)

from_where.m
```


```{r}
ggplot(from_where.m, aes(neighborhood_name, value, fill = rest_neighborhood)) + 
  geom_bar(stat="identity", position = "dodge")+
  labs(y = "Number of restaurants delivering", x = "Neighborhood", fill = "Who delivers is from", title = "From where do restaurants deliver to?")+
  coord_flip()+
  ggsave("fromwhere.png")
```
In this graph we can see how the top 15 neighborhoods for number of restaurants served by, are segmented between the restaurants located in 3 of the top 10 neighborhood for number of restaurants.

```{r}
how_many.m <- melt(how_many)

how_many.m
```
```{r}
ggplot(how_many.m, aes(neighborhood_name, value, fill = neighborhood_name)) + 
  geom_bar(stat="identity", position = "dodge")+
  labs(y = "Number of restaurants delivering", x = "Neighborhood", fill = "Deliver to")+
  coord_flip()+
  ggsave("howmany.png")
```

Based also on this last chart, I would then seggest restaurants that are not on the territory to maybe think of opening stores in the neighborhoods more served, as it may represent a way of, in the long run, reducing costs due to delivery and increasing their revenues as well.

